Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-14 paper/tex/sections/methods.tex

The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate. But the bulge was shown to contain stars with a range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar. To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$

@@

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

@@

For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF. For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.

>>>>

The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate. But the bulge was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar. To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$

@@

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$ {\color{blue} \textbf{Stephen: I thought $2 \times 10^{5}$}?}, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

@@

For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy mass  and only sample from massive stars rather than the full IMF. For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.
